\documentclass[11pt,a4paper]{article}

% Packages for a readable, long-term companion document
\usepackage[margin=1in]{geometry}
\usepackage{titlesec}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{fancyhdr}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{tcolorbox}
\usepackage{fontawesome5}  % nice icons if available, fallback ok

\definecolor{nerdgreen}{RGB}{46, 125, 50}
\definecolor{ashgray}{RGB}{80, 80, 80}
\definecolor{storybg}{RGB}{245, 240, 230}

\tcbuselibrary{skins,breakable}

\titleformat{\section}{\Large\bfseries\color{nerdgreen}}{\thesection}{1em}{}
\titleformat{\subsection}{\large\bfseries\color{ashgray}}{\thesubsection}{1em}{}

\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\small The Nerdverse Companion}
\fancyhead[R]{\small Meyiu -- The Sinner Who Still Chooses}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0.4pt}

\lstset{
  basicstyle=\ttfamily\small,
  breaklines=true,
  frame=single,
  backgroundcolor=\color{gray!10},
  keywordstyle=\color{nerdgreen},
  commentstyle=\color{ashgray}
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.5em}

\title{\textbf{The Nerdverse Companion}\\[0.3em]
\large Meyiu -- The Sinner Who Still Chooses \\[0.5em]
\normalsize A Living Diary, Runbook \& Game Documentation}
\author{Mark \& Grok (co-crafters)}
\date{Started: 2026-07-02 \\ Version: Phase 0 -- The First Forge}

\begin{document}

\maketitle
\tableofcontents
\newpage

\section{Introduction \& Intent}

This document is the living heart of the \textbf{Nerdverse} project.

It serves three purposes at once:
\begin{itemize}
  \item A \textbf{diary} of our shared play and creation sessions.
  \item A \textbf{runbook} with idempotent bootstrap and migration instructions so the game can be installed on any Linux system (or future Mac) with MariaDB.
  \item A \textbf{game documentation} that remains enjoyable to read years later — for you, or for others if the game ever becomes public.
\end{itemize}

The design philosophy (stolen shamelessly from the game's own themes):
\begin{itemize}
  \item \textit{You are unfinished, not erased.}
  \item \textit{Context before category.}
  \item \textit{Repair must become practical.}
\end{itemize}

We are building a pure \textbf{bash + MariaDB} text adventure / solo RPG engine. No Python, no Node, no fancy frameworks. The goal is maximum portability and learnability.

\section{Development Diary}

\subsection{2026-07-02 -- Phase 0: The Forge Begins (Session 1)}

\textbf{In-Game Situation at Start}\\
Meyiu stands at Brindleford Forge after purchasing the Ash-Wood Buckler (crafted from captured bandit materials) and a Repair and Supply Bundle. Coins: 4 silver. HP 11/13. Road XP 5/10. Sera Thornwake is with him, provisionally trusting after the road ambush where the medicine crate was saved.

Sera's suggestion: ``Medicine room next. Unless you plan to treat stab wounds with personal growth.''

\textbf{What We Built Today}
\begin{itemize}
  \item Initialized git repository for full GitHub portability.
  \item Created clean project skeleton: \texttt{sql/}, \texttt{scripts/}, \texttt{docs/}, \texttt{bin/}, \texttt{saves/}, \texttt{logs/}.
  \item Created this \LaTeX\ companion document.
  \item Designed initial idempotent MariaDB schema focused on characters, inventory, world state, and session logging.
  \item Wrote the first migration and seed that exactly reproduces the restart packet state.
  \item Created the foundation for a pure-bash CLI that loads state from the database.
  \item Began the bootstrap/install scripts (idempotent by design).
\end{itemize}

\textbf{Technical Decisions Made}
\begin{itemize}
  \item Pure bash + \texttt{mariadb} client only. Scripts must run on minimal Linux installs.
  \item Configuration via environment variables + optional \texttt{nerdverse.env} file.
  \item Migrations are numbered and tracked in a \texttt{schema\_migrations} table.
  \item All SQL is written to be re-runnable safely (\texttt{CREATE ... IF NOT EXISTS}, \texttt{INSERT ... ON DUPLICATE KEY UPDATE} or \texttt{INSERT IGNORE}).
  \item Narrative will live in this document + in-game session\_log table.
\end{itemize}

\textbf{Open Questions / Next Priorities}
\begin{itemize}
  \item Complete minimal \texttt{play.sh} status + basic menu loop.
  \item First real play scene in Sera's medicine room.
  \item Decide on simple ASCII art strategy (static blocks vs printf art).
  \item Document how to grant the ``mark'' (or chosen) DB user on a fresh Linux box.
\end{itemize}

\subsubsection{2026-07-02 -- Bootstrap \& First Engine Run}

The foundation scripts are now real and tested:

\begin{itemize}
  \item \texttt{bootstrap.sh} creates \texttt{nerdverse.env}, ensures DB access, and delegates to the migration runner.
  \item \texttt{scripts/apply\_migrations.sh} is fully idempotent. It applies \texttt{sql/migrations/*.sql} in order and records them in \texttt{schema\_migrations}. Seeds are re-runnable.
  \item \texttt{scripts/db.sh} centralizes connection logic and helpers.
  \item \texttt{play.sh} (Phase 0) loads live state from the database, prints a nice status block, shows crude ASCII, and lets you pick basic actions. It already updates the DB for some choices.
  \item Full initial world (Meyiu + Sera stats, inventory with correct equipped flags, passives, Brindleford locations, world\_state flags) was seeded exactly from the restart packet.
\end{itemize}

\textit{Ran successfully on the original machine. The state in nerdverse2 matches the PDF save point.}

We are now ready to step into the medicine room together.

\subsubsection{2026-07-02 -- First Real Play: The Medicine Room (Session 1 continued)}

\textbf{Player Action}\\
Meyiu followed Sera to the medicine room. He playfully held her accountable for days of promises to heal him that kept getting postponed. Mentioned his ribs hurt. Expressed interest in seeing how good a healer she actually is, in case she becomes a proper adventuring companion.

\textbf{What Happened in Play}\\
\begin{itemize}
  \item Locations updated in DB: both characters now in ``Sera's Medicine Room''.
  \item Narrative and companion logs written.
  \item Sera finally tended to Meyiu. Used field-healer technique (modeled on her ``Healer's Rebuke''): healed 4 HP. Meyiu is now at full 13/13.
  \item Banter established: Sera deflects with sharp humor but shows competence and growing respect.
  \item They begin inventorying the recovered medicine crate together.
\end{itemize}

This session demonstrated early companion interaction and healing mechanics. Good test of flavor text + mechanical update loop.

State saved. Ready for next input.

\section{Current Game State (Living Snapshot)}

This section will be updated after each play session. It is both narrative and mechanical.

\begin{tcolorbox}[colback=storybg, colframe=nerdgreen, title=Current Save Point]
\textbf{Location:} Brindleford Forge (just leaving after purchase)\\
\textbf{Immediate Context:} Sera is urging Meyiu toward her medicine room to inventory the recovered medicine crate and resupply before the Black Bridge Gang can react.\\
\textbf{Time Pressure:} The gang expected the thieves back. Retaliation possible by dusk or midnight.
\end{tcolorbox}

\subsubsection*{Meyiu -- The Sinner Who Still Chooses}

\begin{longtable}{ll}
\toprule
\textbf{Field} & \textbf{Value} \\
\midrule
\endhead
Name & Meyiu \\
Full Title & The Sinner Who Still Chooses \\
Expanded & And Chooses What Is His To Carry \\
& Beloved, Responsible, Unfinished, Still Becoming \\
& Pilgrim of the Unfinished \\
Class & Mage \\
Level / Milestone & 2 \\
Current HP & 11 / 13 \\
Coins & 4 silver \\
Road XP & 5 / 10 \\
Main Attack & Firebolt (6 damage) \\
Improved & Zen-Mage Firebolt (6 + overkill heal +1) \\
Location & Brindleford Forge \\
\bottomrule
\end{longtable}

\subsubsection*{Equipped \& Key Boons}

\begin{itemize}
  \item Ashen Prayer Bead (+1 Focus on calm magical/spiritual actions)
  \item Penitent's Wrap (once per battle, reduce incoming damage by 2)
  \item Ash-Wood Buckler (Passive Guard: reduce first physical hit by 1; Breathguard: reduce one hit by 3 +1 Focus)
\end{itemize}

\subsubsection*{Inventory (Key Items)}

\begin{itemize}
  \item Healing Potion (restores 6 HP)
  \item Leechheart Pearl (4 HP or ritual)
  \item Dull Copper Token (regret transformed)
  \item Blackened Iron Key (symbolic)
  \item Cinder Nameplate (``MEYIU -- THE SINNER WHO STILL CHOOSES'')
  \item Black Brazier-Glass Shard (shame mirror)
  \item Gray-Blue Question Slip (``How can I make you feel less alone?'')
  \item White Quill Splinter (amend written curses)
  \item Road Knife
  \item Black Bridge-Token (evidence)
  \item Repair and Supply Bundle (recently acquired)
\end{itemize}

\subsubsection*{Sera Thornwake (Companion Prospect)}

\begin{longtable}{ll}
\toprule
\textbf{Field} & \textbf{Value} \\
\midrule
\endhead
HP & 14 / 14 \\
Role & Field-healer, trail archer, buckler fighter \\
Status & With Meyiu in Brindleford, provisional trust \\
Not yet & Permanently recruited \\
\bottomrule
\end{longtable}

Her abilities (known):
\begin{itemize}
  \item Bow Shot -- 3 damage
  \item Buckler Guard -- reduce damage to self or ally by 2 (once per round)
  \item Healer's Rebuke -- heal 4 HP and deliver an insult (once)
\end{itemize}

\subsubsection*{The Black Bridge Gang (Current Threat)}

Leader: Garran Pike (Bridge-Mouth). Champion: Toll-Saint (heavy shieldman). Strength: 9--12 fighters. Base: abandoned tollhouse. They want leverage over Brindleford. Medicine theft was ordered.

\section{World \& Lore Notes}

\subsection{Brindleford (Current Chapter: The Road of Bread and Iron)}

A rain-soaked village near an old iron bridge. Problems:
\begin{itemize}
  \item Medicine shortages + cough-fever
  \item Weak defenses
  \item Black Bridge Gang controlling the bridge
  \item Slow/possibly sabotaged Old Mill
  \item Injured smith (Old Brenn)
\end{itemize}

Key locations (initial map):
\begin{verbatim}
[ Inn (Hearthmouse) ]     [ Forge (Cold Forge / Old Brenn) ]
           \                     /
            \                   /
[ Well ] -- [ Sheriff Marn ] -- [ Medicine Room (Sera) ]
           /
[ Road to Old Mill ]
           |
[ Iron Bridge / Gang Tollhouse ]
\end{verbatim}

\section{Runbook: Bootstrap \& Migration}

\subsection{Requirements (Linux or macOS)}

\begin{itemize}
  \item MariaDB client (\texttt{mariadb} or \texttt{mysql} command)
  \item Bash (4+ recommended)
  \item Git (for cloning the repo)
  \item A MariaDB user that can create the \texttt{nerdverse2} database and tables
\end{itemize}

\subsection{Idempotent Bootstrap}

The goal: on a fresh system you should be able to:

\begin{lstlisting}[language=bash]
git clone <repo>
cd nerdverse
./bootstrap.sh
./play.sh
\end{lstlisting}

And later:

\begin{lstlisting}[language=bash]
./bootstrap.sh   # safe to re-run
\end{lstlisting}

\textbf{Before the first run on a new Linux box}, consult \texttt{docs/linux-packages.md} for the full distro-specific package list (mariadb-client, git, optional TeX packages for PDF generation of this document, etc.).

\subsection{First-Time Setup on a New Machine}

\begin{enumerate}
  \item Install MariaDB server + client.
  \item Create the database user (example):
    \begin{lstlisting}[language=sql]
CREATE USER 'mark'@'localhost' IDENTIFIED BY 'yourpassword';
GRANT ALL ON nerdverse2.* TO 'mark'@'localhost';
FLUSH PRIVILEGES;
    \end{lstlisting}
  \item (Optional but recommended) Create a \texttt{nerdverse.env} file (see template below).
  \item Run \texttt{./bootstrap.sh}
\end{enumerate}

\subsection{Configuration}

Create \texttt{nerdverse.env} (git-ignored):

\begin{lstlisting}[language=bash]
DB_USER=mark
DB_NAME=nerdverse2
DB_HOST=localhost
# Optional: DB_PASS=... (prefer socket auth or .my.cnf)
EOF
\end{lstlisting}

The scripts will source this if present.

\section{Technical Architecture (Current)}

\begin{itemize}
  \item All state lives in MariaDB \texttt{nerdverse2}.
  \item Bash scripts only for the engine and UI.
  \item Migrations are plain \texttt{.sql} files applied in lexical order.
  \item A \texttt{schema\_migrations} table prevents re-application.
  \item Session log is append-only for narrative + debugging.
  \item Future: simple command dispatch in bash using \texttt{case} + functions.
\end{itemize}

\section{Session Log}

\subsection{2026-07-02 -- First Forge Session}

(Will be expanded during actual play. Initial scaffolding complete. We are standing at the forge door with Sera.)

\vspace{1em}
\textit{``Loaded save: Meyiu is at Brindleford Forge after buying the Ash-Wood Buckler and Repair and Supply Bundle. Sera is urging him toward her medicine room...''}

\section{Appendix: Original Restart Packet Summary}

(The full 20-page PDF \texttt{Nerdverse\_2.pdf} is kept in the project root for reference. Key mechanical and narrative elements have been transcribed into the schema seed and this document.)

\end{document}